### 2008-08-03 doc/backend_interface/Backends.tex
backends doc update

\begin{quote}
Parses a config file. It returns exit status 1 if the file cannot
be read, or 0 otherwise. Badly formed lines are silently ignored.
Option values can be surrounded by single quotes or double quotes.
Values without quotes are also accepted. Multi-valued options are
not supported currently. Only the last defined value is retained. 
\end{quote}
\texttt{config\_update\_from\_section <section\_name>}

@@

\texttt{config\_update\_from\_section common}

\texttt{config\_update\_from\_section grid-manager}

\texttt{config\_update\_from\_section infosys}

@@

The information collector scripts are divided between several separate scripts:
\begin{itemize}
\item \texttt{cluster+qju.pl} - driver for information collection. It calls all other information collectors and prints results in XML. The information collection is done by one single invocation of this script
\item \texttt{InfoCollector.pm} - base class for all information collectors (i.e.: all files \texttt{*Info.pm})
\item \texttt{InfoChecker.pm} - used by InfoCollector to validate options and results against a simple 'schema' (not XML Schema)
\item \texttt{GMJobsInfo.pm} - collects information about jobs from grid manager status files
\item \texttt{HostInfo.pm} - collects other information that can be collected on the front end (hostname, software version, disk space for users, installed certificates, Runtime environments ...)
\item \texttt{LRMSInfo.pm} - collects information that is LRMS specific (queues, jobs, local user limits ...)
\item \texttt{BATCH\_SYSTEM\_NAME.pm} - plugins for LRMSInfo. Only Fork, SGE and PBS are updated to the new framework
\item \texttt{ARC0ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the classic NG schema
\item \texttt{ARC1ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the GLUE2 schema
\item \texttt{ARC0ClusterSchema.pm} - description of the info produced by ARC0ClusterInfo
\item \texttt{ARC1ClusterSchema.pm} - description of the info produced by ARC1ClusterInfo
\end{itemize}

@@

The LRMS module should implement four functions as defined by the
\texttt{LRMS.pm}: \texttt{Cluster\_info}, that provides general information
about the local cluster, \texttt{Queue\_info}, that provides information
about a specified queue, \texttt{Jobs\_info} that gives information
about a list of specified jobs, and finally \texttt{user\_info} that
gives information about a grid user mapped to a local UNIX account.
All the functions are called with a hash containing the contents of
arc.conf.

\subsubsection{cluster\_info}

\texttt{Cluster\_info} is called only with the config hash. It should
then return an associative array with the following keys and the appropriate
value.

\begin{tabular}{|c|c|}
\hline 
key&
value\tabularnewline
\hline
\hline 
lrms\_type&
the type of LRMS e.g PBS\tabularnewline
\hline 
lrms\_version&
the version of the LRMS\tabularnewline
\hline 
totalcpus&
total number of CPUs in the cluster\tabularnewline
\hline 
queuedcpus&
total number of CPUs requested by LRMS queuing jobs (both grid and
non-grid)\tabularnewline
\hline 
usedcpus&
CPUs in the LRMS that are currently in use either by grid or non-grid
jobs\tabularnewline
\hline 
cpudistribution&
number of CPUs in a node and number of each type e.g. {}``8cpu:5
2cpu:100''\tabularnewline
\hline
\end{tabular}

\subsubsection{queue\_info}

In addition to the config \texttt{queue\_info} is called with the
name of the queue to get information on. The result should take the
following form.

\begin{tabular}{|c|c|}
\hline 
key&
value\tabularnewline
\hline
\hline 
status&
available slots in queue, negative number signals error\tabularnewline
\hline 
maxrunning&
limit on number of running jobs\tabularnewline
\hline 
maxqueuable&
limit on number of jobs queued on this queue\tabularnewline
\hline 
maxuserrun&
limit on number of running jobs per user\tabularnewline
\hline 
maxcputime&
limit on maximum CPU time for a job in this queue\tabularnewline
\hline 
mincputime&
limit on minimum CPU time for a job in this queue\tabularnewline
\hline 
defaultcput&
default CPU time limit for a job in this queue\tabularnewline
\hline 
maxwalltime&
limit on maximum wall time for a job in this queue\tabularnewline
\hline 
minwalltime&
limit on minimum wall time for a job in this queue\tabularnewline
\hline 
defaultwallt&
default wall time limit for a job in this queue\tabularnewline
\hline 
running&
number of CPUs used by running jobs (both grid and non-grid) in the
queue\tabularnewline
\hline 
queued&
CPUs requested by queuing jobs in the queue\tabularnewline
\hline 
totalcpus&
number of CPUs available to the queue\tabularnewline
\hline
\end{tabular}

\subsubsection{jobs\_info}

Like the rest the first argument is the config hash, then comes the
queue name and finally a list of job ids. Once again an associative
mapping should be made for each job. The key value pairs are:

\begin{tabular}{|c|c|}
\hline 
key&
value\tabularnewline
\hline
\hline 
status&
LRMS jobstatus mapping%
\footnote{LRMS job states mapping is described in~\cite{is} %
}:Running->'R', Queued->'Q', Suspended->'S', Exiting->'E', Other->'O'\tabularnewline
\hline 
rank&
the job's position in the LRMS queue\tabularnewline
\hline 
mem&
the memory usage of the job in kBs\tabularnewline
\hline 
walltime&
consumed wall-time in minutes\tabularnewline
\hline 
cputime&
consumed CPU-time in minutes\tabularnewline
\hline 
reqwalltime&
wall-time requested by job in minutes\tabularnewline
\hline 
reqcputime&
CPU-time requested by job in minutes\tabularnewline
\hline 
nodes&
list of execution hosts\tabularnewline
\hline 
comment&
array of string comments about the job in LRMS, can be an empty array\tabularnewline
\hline
\end{tabular}

\subsubsection{user\_info}

\texttt{Users\_info} is given the config hash, a queue name and a
list of local UNIX accounts (UIDs). It should then return an associative
array containing for each UID the number of free CPUs available for
that local account on the given queue and the number of queued jobs
on that queue.

\begin{tabular}{|c|c|}
\hline 
key&
value\tabularnewline
\hline
\hline 
freecpus&
number of freely available CPUs with their time limits in minutes
(see nordugrid-authuser-freecpus in~\cite{is})\tabularnewline
\hline 
queuelength&
estimated queue length for the specified user\tabularnewline
\hline
\end{tabular}

>>>>

\begin{quote}
Parses a config file. It returns exit status 1 if the file cannot
be read, or 0 otherwise. Badly formed lines are silently ignored.
Option values can be surrounded by single quotes or double quotes.
Values without quotes are also accepted. Multi-valued options are
not supported currently. Only the last defined value is retained. 
\end{quote}
\texttt{config\_import\_section <section\_name>}

@@

\texttt{config\_import\_section common}

\texttt{config\_import\_section grid-manager}

\texttt{config\_import\_section infosys}

@@

The information collector scripts are divided between several separate scripts:
\begin{itemize}
\item \texttt{cluster+qju.pl} - driver for information collection. It calls all other information collectors and prints results in XML. The information collection is done by one single invocation of this script
\item \texttt{InfoCollector.pm} - base class for all information collectors (i.e.: all files \texttt{*Info.pm}).
\item \texttt{InfoChecker.pm} - used by InfoCollector to validate options and results against a sort of ``schema'', as implemented by \texttt{InfoChecker.pm}.
\item \texttt{GMJobsInfo.pm} - collects information about jobs from grid manager status files
\item \texttt{HostInfo.pm} - collects other information that can be collected on the front end (hostname, software version, disk space for users, installed certificates, Runtime environments ...)
\item \texttt{LRMSInfo.pm} - collects information that is LRMS specific (queues, jobs, local user limits ...) by calling the appropriate LRMS plugin. It also does validation of input options to the plugin and of the data returned by the plugin. 
\item \texttt{BATCH\_SYSTEM\_NAME.pm} - plugins for LRMSInfo. Only Fork, SGE and PBS are updated to the new framework
\item \texttt{ARC0ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the classic NG schema
\item \texttt{ARC1ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the GLUE2 schema
\item \texttt{ARC0ClusterSchema.pm} - ``schema'' of the info produced by ARC0ClusterInfo
\item \texttt{ARC1ClusterSchema.pm} - ``schema'' of the info produced by ARC1ClusterInfo
\end{itemize}

@@

Each LRMS module should implement two functions: \texttt{lrms\_info} and
\texttt{get\_lrms\_options\_schema}.

\subsubsection{get\_lrms\_options\_schema}

This function is called without arguments and should return a ``schema'' hash
declaring the configuration options specific for this LRMS plugin. This
``schema'' conforms to the format understood by \texttt{InfoChecker.pm} and is
used to validate input options by \texttt{LRMSInfo.pm}.

\subsubsection{lrms\_info}

\texttt{lrms\_info} returns all LRMS specific information. This
includes information about the cluster, queues, jobs and local users. The
function is called with an options hash of hashes. It should then return an
hash of hashes with the following keys and the appropriate value.

\begin{table}
\caption{The \texttt{lrms\_info} hash} \label{t:lrms_info}
\begin{center}
\begin{tabular}{|c|c|}
\hline
key & value\\
\hline \hline
lrms\_type & the type of LRMS e.g PBS\\
\hline
lrms\_version & the version of the LRMS\\
\hline
totalcpus & total number of CPUs in the cluster\\
\hline
queuedcpus & total number of CPUs requested by LRMS queuing jobs (both grid and
non-grid)\\
\hline
usedcpus & CPUs in the LRMS that are currently in use either by grid or
non-grid jobs\\
\hline
cpudistribution & number of CPUs in a node and number of each type e.g.
{}``8cpu:5 2cpu:100''\\
\hline
queues & a hash with keys being queue names and values being
\texttt{queue\_info} hashes as described in table \ref{t:queue_info} \\
\hline
jobs & a hash with keys being LRMS job IDs and values being
\texttt{jobs\_info} hashes as described in table \ref{t:jobs_info} \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{The \texttt{queue\_info} hash}
\label{t:queue_info}
\begin{center}
\begin{tabular}{|c|c|}
\hline
key & value\\
\hline \hline
status & available slots in queue, negative number signals error\\
\hline
maxrunning & limit on number of running jobs\\
\hline
maxqueuable & limit on number of jobs queued on this queue\\
\hline
maxuserrun & limit on number of running jobs per user\\
\hline
maxcputime & limit on maximum CPU time for a job in this queue in minutes\\
\hline
mincputime & limit on minimum CPU time for a job in this queue in minutes\\
\hline
efaultcput & default CPU time limit for a job in this queue in minutes\\
\hline
maxwalltime & limit on maximum wall time for a job in this queue in minutes\\
\hline
minwalltime & limit on minimum wall time for a job in this queue in minutes\\
\hline
defaultwallt & default wall time limit for a job in this queue in minutes\\
\hline
running & number of CPUs used by running jobs (both grid and non-grid) in the
queue\\
\hline
queued & number of CPUs requested by queuing jobs in the queue\\
\hline
totalcpus & number of CPUs available to the queue\\
\hline
users & a hash with keys being local UNIX user names and values being
\texttt{users\_info} hashes as described in table \ref{t:users_info} \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{The \texttt{users\_info} hash}
\label{t:users_info}
\begin{center}
\begin{tabular}{|c|c|}
\hline
key & value\\
\hline \hline
freecpus & number of freely available CPUs with their time limits in minutes
(see ComputingService.FreeSlotsWithDuration in\cite{glue2})\\
\hline
queuelength & estimated queue length for the specified user\\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{The \texttt{jobs\_info} hash}
\label{t:jobs_info}
\begin{center}
\begin{tabular}{|c|c|}
\hline
key & value\\
\hline \hline
status & LRMS jobstatus mapping\footnotemark[1]:
Running->'R', Queued->'Q', Suspended->'S', Exiting->'E', Other->'O'\\
\hline
rank & the job's position in the LRMS queue\\
\hline
mem & the memory usage of the job in kBs\\
\hline
walltime & consumed wall-time in minutes\\
\hline
cputime & consumed CPU-time in minutes\\
\hline
reqwalltime & wall-time requested by job in minutes\\
\hline
reqcputime & CPU-time requested by job in minutes\\
\hline
nodes & list of execution hosts\\
\hline
comment & array of string comments about the job in LRMS, can be an empty
array\\
\hline
\end{tabular}
\footnotetext[1]{LRMS job states mapping is described in\cite{is}}
\end{center}
\end{table}
